|

### 2023-05-31 manuscript/Chapter2-appendix3.Rmd
update appendix 3

# Extract the fixed effects from the model
eff_tab <- data.table(fixef(fit), keep.rownames = TRUE)
eff_tab <- eff_tab[, c(1, 2, 4:5)]

# Rename variables
setnames(
  eff_tab,
  c("rn", "Q2.5", "Q97.5"),
  c("parameter", "lower_ci", "upper_ci")
)

# Add a column that specifies the experience level
eff_tab[parameter %like% "novice", xp_level := "novice"]
eff_tab[parameter %like% "interm", xp_level := "intermediate"]
eff_tab[parameter %like% "advanced", xp_level := "advanced"]

# Back transform success
eff_tab[
  parameter %like% "success",
  c(2:4) := lapply(.SD, function(x) {plogis(x)}),
  .SDcols = c(2:4)
]

# Back transform sigma
eff_tab[
  parameter %like% "sigma",
  c(2:4) := lapply(.SD, function(x) {exp(x)}),
  .SDcols = c(2:4)
]

# Round values to 3 digits
eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 2)]

# Reorganize the table ------------------------------------------------------

# reorder columns, and then rows based on xp level
eff_tab <- eff_tab[, c(5, 1:4)]
setorder(
  eff_tab,
  cols = -"xp_level"
)

# Create trait column
eff_tab[
  , trait := rep(c(
    "predator speed", "predator speed",
    "prey speed", "prey speed", "hunting success"),
    6
  )
]

# Rename parameter
eff_tab[
   , parameter := rep(
      c(
         rep(c("intercept (mean)", "intercept (sigma)"), 2),
         "intercept (mean)",
         rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
         "match duration (mean)"
      ),
      3
   )
]

# Paste upper and lower ci with estimate
eff_tab[, estimate := paste(format(Estimate, digits = 2), "(")]
eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
eff_tab[, estimate := paste(estimate, ",", sep = "")]
eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
eff_tab[, estimate := paste(estimate, ")", sep = "")]
eff_tab[, c("Estimate", "lower_ci", "upper_ci") := NULL]

# Reshape
eff_tab <- dcast(
  eff_tab,
  trait + parameter ~ xp_level,
  value.var = "estimate"
)

# Reorder columns
eff_tab <- eff_tab[, c(1, 2, 5, 4, 3)]

# Reorder rows
table <- eff_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]

# Because I can't align hunting success properly
table[10, 1] <- " "

@@

@@

  # Table caption
  set_caption(
    caption = "Table S1. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success. The coefficients are from the model that includes the outlier.",
    style = "Table Caption"
  ) %>%

@@

@@

# Custom theme
my_theme <- function(x, ...) {
  x <- colformat_double(x, big.mark = " ",
                        decimal.mark = ".",
                        digits = 2)
  x <- set_table_properties(x, layout = "autofit")
  x <- border_remove(x)
  std_border <- fp_border(width = 1, color = "black")
  x <- hline_top(x, part = "all", border = std_border)
  x <- hline_bottom(x, part = "all", border = std_border)
  autofit(x)
}

@@

tab3 <-

@@

  # Add footnote
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
      as_sup("\nc "),
      "The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization. For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
    ),
    ref_symbols = " "
  ) %>%

  # Add table caption
  set_caption(
    caption = "Table S2. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success. The coefficients are from the model that includes the outlier.",
    style = "Table Caption"
  ) %>%

@@

tab3 <- autofit(tab3)

tab3

@@

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM. The test is displayed on the y axis (i.e. whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience level groups that are being compared. The results are from the model that includes the outlier."}

@@

```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis. The results are from the MDHGLM that includes the outlier."}

>>>>

# Extract the fixed effects posterior samples
b_draws <- data.table(
  as_draws_df(
    fit, variable = "^b_", regex = TRUE
  )
)

b_draws[, c(34:36) := NULL]

# Back-transform the parameters ----------------------------------------------

# Take the exponent of sigma parameters
b_draws[
  , c("b_sigma_speednovice_Intercept",
      "b_sigma_speedinterm_Intercept",
      "b_sigma_speedadvanced_Intercept",
      "b_sigma_preyspeednovice_Intercept",
      "b_sigma_preyspeedinterm_Intercept",
      "b_sigma_preyspeedadvanced_Intercept",
      "b_sigma_speednovice_Zprey_avg_rank",
      "b_sigma_speedinterm_Zprey_avg_rank",
      "b_sigma_speedadvanced_Zprey_avg_rank",
      "b_sigma_preyspeednovice_Zprey_avg_rank",
      "b_sigma_preyspeedinterm_Zprey_avg_rank",
      "b_sigma_preyspeedadvanced_Zprey_avg_rank"
  )
  := lapply(.SD, function(x) {exp(x)}),
  .SDcols = c(
    "b_sigma_speednovice_Intercept",
    "b_sigma_speedinterm_Intercept",
    "b_sigma_speedadvanced_Intercept",
    "b_sigma_preyspeednovice_Intercept",
    "b_sigma_preyspeedinterm_Intercept",
    "b_sigma_preyspeedadvanced_Intercept",
    "b_sigma_speednovice_Zprey_avg_rank",
    "b_sigma_speedinterm_Zprey_avg_rank",
    "b_sigma_speedadvanced_Zprey_avg_rank",
    "b_sigma_preyspeednovice_Zprey_avg_rank",
    "b_sigma_preyspeedinterm_Zprey_avg_rank",
    "b_sigma_preyspeedadvanced_Zprey_avg_rank"
  )
]

# plogis for the success parameters
b_draws[
  , c("b_successnovice_Intercept",
      "b_successinterm_Intercept",
      "b_successadvanced_Intercept",
      "b_successnovice_Zgame_duration",
      "b_successinterm_Zgame_duration",
      "b_successadvanced_Zgame_duration",
      "b_successnovice_Zprey_avg_rank",
      "b_successinterm_Zprey_avg_rank",
      "b_successadvanced_Zprey_avg_rank"
  )
  := lapply(.SD, function(x) {plogis(x)}),
  .SDcols = c(
    "b_successnovice_Intercept",
    "b_successinterm_Intercept",
    "b_successadvanced_Intercept",
    "b_successnovice_Zgame_duration",
    "b_successinterm_Zgame_duration",
    "b_successadvanced_Zgame_duration",
    "b_successnovice_Zprey_avg_rank",
    "b_successinterm_Zprey_avg_rank",
    "b_successadvanced_Zprey_avg_rank"
  )
]

fixef_tab <- melt(
  b_draws,
  variable.name = "parameter"
)

# Summarize the values (medians + 95% CI) -------------------------------------

# Summarize values
fixef_tab[, ":=" (median = median(value),
                  lower_ci = lower_interval(value),
                  upper_ci = upper_interval(value)),
          by = .(parameter)]

fixef_tab <- unique(fixef_tab[, .(parameter, median, lower_ci, upper_ci)])
fixef_tab[, c(2:4) := round(fixef_tab[, c(2:4)], digits = 2)]

# Add a column that specifies the experience level
fixef_tab[parameter %like% "novice", xp_level := "novice"]
fixef_tab[parameter %like% "interm", xp_level := "intermediate"]
fixef_tab[parameter %like% "advanced", xp_level := "advanced"]

# Paste upper and lower ci with estimate
fixef_tab[, estimate := paste(format(median, digits = 2), "(")]
fixef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
fixef_tab[, estimate := paste(estimate, ",", sep = "")]
fixef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
fixef_tab[, estimate := paste(estimate, ")", sep = "")]
fixef_tab[, c("median", "lower_ci", "upper_ci") := NULL]

# reorder columns, and then rows based on xp level
setorder(
  fixef_tab,
  cols = -"xp_level"
)

# Create trait column
fixef_tab[, trait := ""][
  parameter %like% "success", trait := "hunting success"][
    parameter %like% "speed", trait := "predator speed"][
      parameter %like% "preyspeed", trait := "prey speed"
      ]

# Rename parameter column
fixef_tab[
  , parameter := rep(
    c(
      rep(c("intercept (mean)", "intercept (sigma)"), 2),
      "intercept (mean)",
      rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
      "match duration (mean)", "prey rank (mean)"
    ),
    3
  )
]

# Reshape
fixef_tab <- dcast(
  fixef_tab,
  trait + parameter ~ xp_level,
  value.var = "estimate"
)

# Reorder columns and rows
fixef_tab <- fixef_tab[, c(1, 2, 5, 4, 3)]
table <- fixef_tab[c(4, 6, 5, 7, 8, 10, 9, 11, 1, 2, 3)]

# Because I can't align the rows properly
# in the flextable object
table[c(2:4, 6:8, 10, 11), 1] <- " "

@@

tab1 <-

@@

  # Table caption
  set_caption(
    caption = "Table S1. Posterior medians and 95% HPD intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success. The coefficients are from the model that includes the outlier.",
    style = "Table Caption"
  ) %>%

@@

tab1

@@

# Custom theme
my_theme <- function(x, ...) {
  x <- colformat_double(x, big.mark = " ",
                        decimal.mark = ".",
                        digits = 2)
  x <- set_table_properties(x, layout = "autofit")
  x <- border_remove(x)
  std_border <- fp_border(width = 1, color = "black")
  x <- hline_top(x, part = "all", border = std_border)
  x <- hline_bottom(x, part = "all", border = std_border)
}

@@

@@

  # Add footnote
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale.",
      as_sup("\nb "),
      "The standard deviation values on the mean part of the equation indicate, for all traits, among individual differences in mean behaviour, prey encountered, and success.",
      as_sup("\nc "),
      "The standard deviation values on the dispersion part of the equation (i.e. sigma) for predator speed indicate among individual differences in behavioural specialization. For prey speed, they indicate among individual differences in the variability of prey encounters."
    ),
    ref_symbols = " "
  ) %>%

  # Add table caption
  set_caption(
    caption = "Table S2. Posterior medians and 95% HPD intervals of the random effect standard deviations estimated by the MDHGLM of predator speed, prey speed, and predator hunting success. The coefficients are from the model that includes the outlier.",
    style = "Table Caption"
  ) %>%

@@

@@

```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences between the parameter values of each predator experience level predicted by the MDHGLM along with their and 95% HPD intervals. The test is displayed on the y axis (i.e. whether the experience level of interest has a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience levels being compared. The results are from the model that includes the outlier."}

@@

```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences in the correlations of players when they were advanced vs novice along with their 95% HPD intervals. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis. Positive values indicate that the correlation was greater when predators where advanced, while negative values indicate that the correlation was greater when predators where novices. The results are from the MDHGLM that includes the outlier."}
